\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\definecolor{linkcolour}{RGB}{0, 149, 255}
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolour
}

\begin{document}

\title{\textit{Awakening}}
\author{Luna Y.}
\date{
    SFWRENG 3GB3 -- Assignment 5\\[0.25cm]
    \today
}
\maketitle

\tableofcontents

\section{Basic Information}

As specified in the assignment outline, this game will be built off of Unity's RPG Creator Kit.
The game itself will be one where the player must gather materials to craft items and use them to defeat enemies.
Different enemies will have different types, and different types of items (weapons, armour, etc.) will be more or
less effective against different types of enemies (somewhat similar to type advantages from the \textit{Pokemon} games).

As for challenges, there will resource accumulation challenges, stealth challenges, as well as survival and reduction of enemy forces
at the very least. There are also elements of spatial awareness challenges, as well as speed and reaction time challenges.
The specific details of these challenges will be explained in the later sections of this document.

\section{Gameplay}

In the level, there are enemies scattered across the map that have predetermined movement patterns. Enemies, as well
as the player, each have their own health values, which can be decreased by being attacked. Players kill enemies
by reducing their health to zero, and players die when \textit{their} health reaches zero. The goal is to defeat
all the enemies, while keeping the player avatar alive. If enemies have set movement patterns,
this also adds an element of a pattern recognition challenge.

However, combat is not just as simple as running up to an enemy and hitting it until it dies. Each enemy has a particular
``type'': armoured, magical, unarmoured, and incorporeal, and the player's weapons can either be blunt, piercing, or magical.
Strengths and weaknesses are given in the following table, where ``Weak'' indicates an armour type's weakness to an attack,
``Resist'' indicates that an armour type is highly resistant against an attack, ``Invulnerable'' indicates that attacks of
that type will do zero damage to the corresponding armour type, and ``Normal'' indicates no modifier:
\begin{center}
    \begin{tabular}{|c|c|c|c|c|}
        \hline
        & Armoured & Magical & Unarmoured & Incorporeal\\
        \hline
        Blunt & Resist & Normal & Normal & Invulnerable\\
        Piercing & Weak & Normal & Normal & Invulnerable\\
        Magical & Normal & Resist & Normal & Weak\\
        \hline
    \end{tabular}
\end{center}
The player starts out with no weapon equipped, so they must first gather resources to craft one. Players store all
crafted weapons in their inventory, and different weapons can be equipped or unequipped at will.
While the player has no weapon, they are unable to attack enemies, which means they must remain in stealth,
and avoid combat with enemies to gather resources for their first weapon.

While crafting, the player needs to be able to keep track of their surroundings, and also quickly stop crafting
and react to any changes if necessary. As such, the crafting itself will be rather simple, and should be interruptible
as well. Crafting different weapons will require different amounts of various types of materials, which must be gathered
by the player during gameplay. Gathering materials is as simple as moving next to a material node on the map and interacting
with it to gather the material. Gathering items should require a certain amount of time,
which encourages the player to not do so while there are enemies nearby that might interrupt them. Alternatively, the player
might choose to stand still and gather an item they need even if enemies are nearby, though they will likely take damage
from doing so; in some cases, they might feel that the trade-off is worth it. Crafting in this game will be somewhat similar
to how crafting works in \textit{Starbound}; each crafting recipe requires a list of materials, though unlike \textit{Starbound},
there is no time requirement. This directly contributes to the resource accumulation and spatial awareness challenges.
Resource accumulation is fairly straightforward, and spatial awareness comes from the player needing to track where they have been,
where things are in the map, what enemies are nearby, and so on.

For simplicity, all combat will be performed using ranged attacks. Each weapon has a damage and type (see table above)
associated with it, and the exact damage done to an enemy is further modified by any damage bonuses or penalties
(which are determined by type matchings). For simplicity, the player is not weak or resistant to any particular type of damage.
Additionally, rather than free targeting of attacks, the mechanic of ``tab targeting'', commonly seen in MMORPGs like \textit{Final Fantasy XIV},
will be borrowed, so that players will select an explicit target for their attacks. At all times, the player should also be able
to see a visualization of each enemy's aggression radius (outside of which the enemy will not attack the player),
which should help them plan their routes for gathering materials, and finding safe places to craft.
Inadvertently, having these ranged attacks also introduces a speed and reaction time challenge, as the player is able
to dodge enemy attacks if they move out of the way before one hits them.

\section{Aesthetics}

The story/lore of the game is that the player is some kind of adventurer/hero who has awoken in an underground setting (either a cave system
or castle) filled with enemies, and they must escape after defeating all the enemies near them. This lore will be presented
either as an introduction pop-up or in the instructions.

The visual and musical styles should match the story. That is, the visuals should be darker and more ``gloomy'' while still
being somewhat light-hearted (the goal isn't for the game to look depressing or dull), while the music used should be more
instrumental, with a darker/more sombre feeling, as opposed to bright and cheerful.

\section{Player Experience}

The initial section of gameplay should evoke a sense of suspense and ``sneakiness'', as the player must navigate the map
and gather resources without being spotted by enemies. The player should feel rather weak at this point, as they have no
method of fighting back against enemies. Since the player will likely feel frustrated if they make a mistake and are permanently
followed by an enemy that spotted them, the player should be able to escape enemies by running away. Doing so should be fairly easy
as enemies will not chase after the player.

During combat, the mood should be more energetic, which can be supported by a change in music (just like in \textit{Gloamwardens}).
The appearance of enemies will allow the player to make some educated guesses about how strong those enemies are,
though they will not have exact information. This encourages the player to be more careful, as they don't know exactly
how much stronger an enemy might be.

The player should feel a sense of progression throughout the level as they manage to create more powerful weapons.
At the beginning, they should feel relatively weak, while by the end, they should feel powerful.
This is supported by the level design of the game; in the starting area, the player can only gather enough materials
to create a basic ancient sling, which is the weakest weapon. To acquire the materials needed for stronger weapons,
they must reach the second area, which is guarded by considerably more powerful enemies. This also presents a choice
for the player, where they can rush the second area to access more powerful weapons earlier at the risk of taking
considerably more damage, or they can play it safe, gather resources to craft a weaker weapon, and clear out enemies
in the starting area before moving on. The presence of an incorporeal wraith enemy also presents a barrier to player
progression; physical weapons cannot damage it, so they must craft an ice staff in order to win the game.

\section{Changes From Original}

It was decided that enemy aggression radii should be visible at all times, rather than only when one is targeted,
as this gives the player more information, even if it makes the screen a bit more cluttered. If the original idea
was kept, the player could have to constantly cycle through a lot of enemies to make sure they don't get spotted
if a lot of them were on the screen at the same time, which is tedious and potentially frustrating.

Additionally, the time requirement for crafting was removed (though the one for gathering remains), since it already
takes some time to open the crafting menu, select a recipe, and press craft; adding a further time requirement on top
of that which could also potentially be interrupted by enemy attacks could end up being too frustrating for the player.

It was also decided to not give the player exact information about an enemy, as the sense of uncertainty or even trepidation
that this brings fits better with the game's themes.

\section{Works Used}

This project uses Unity's 2D RPG Creator Kit as a base (i.e. code, art, and audio from this kit are used).
It can be found in the \href{https://assetstore.unity.com/packages/templates/tutorials/creator-kit-rpg-149309}{Unity Asset Store}.
The Creator Kit also includes third-party assets such as Cinemachine, the MisterPixel font, Web-GL Noise, and EmojiOne.

% \subsection{Concepts}

\subsection{Code}

This project includes code assets from the previous assignments, such as the music player.

The game also uses the \href{https://arongranberg.com/astar/}{A* Pathfinding Project} as its pathfinding algorithm,
which uses the \href{https://unity3d.com/legal/as_terms}{Standard Unity Asset Store EULA}.

\subsection{Art}

\textbf{\textit{Dungeon Crawl Stone Soup}}
\begin{itemize}
    \item The game uses main and supplementary sprites from \textit{Dungeon Crawl Stone Soup}, hosted \href{https://opengameart.org/content/dungeon-crawl-32x32-tiles}{here}
        and \href{https://opengameart.org/content/dungeon-crawl-32x32-tiles-supplemental}{here}, respectively.
    \item These assets are in the public domain, under the \href{https://creativecommons.org/publicdomain/zero/1.0/}{CC0 1.0} license.
\end{itemize}

\textbf{RPG Worlds Caves}
\begin{itemize}
    \item The game uses Szadi's RPG Worlds Caves tileset, hosted on the \href{https://assetstore.unity.com/packages/2d/environments/rpg-worlds-caves-167274}{Unity asset store}.
    \item These assets are licensed under the \href{https://unity3d.com/legal/as_terms}{Standard Unity Asset Store EULA}.
\end{itemize}

% \subsection{Fonts}

% \textbf{Alegreya SC}
% \begin{itemize}
%     \item Licensed under OFL
%     \item Sourced from \href{https://fonts.google.com/specimen/Alegreya+SC}{Google Fonts}
% \end{itemize}

% \textbf{IM Fell Double Pica SC}
% \begin{itemize}
%     \item Licensed under OFL
%     \item Sourced from \href{https://fonts.google.com/specimen/IM+Fell+Double+Pica+SC}{Google Fonts}
% \end{itemize}

\subsection{Audio}

All sound effects are from the RPG Creator Kit. This project also includes the following music tracks:

Dreamy Piano Fantasy  by Rafael Krux\\
Link: \url{https://filmmusic.io/song/5635-dreamy-piano-fantasy-}\\
License: \url{https://filmmusic.io/standard-license}

Electric Cellos  by Rafael Krux\\
Link: \url{https://filmmusic.io/song/5636-electric-cellos-}\\
License: \url{https://filmmusic.io/standard-license}

Midnight Magic  by Rafael Krux\\
Link: \url{https://filmmusic.io/song/5426-midnight-magic-}\\
License: \url{https://filmmusic.io/standard-license}

Nightmare by Alexander Nakarada\\
Link: \url{https://filmmusic.io/song/4890-nightmare}\\
License: \url{https://filmmusic.io/standard-license}

The Return by Alexander Nakarada\\
Link: \url{https://filmmusic.io/song/4914-the-return}\\
License: \url{https://filmmusic.io/standard-license}

% Dungeon Crawl Stone Soup assets, Szadi RPG Cave and Rogue Castle.

\end{document}